Deciding to Disclose

### 2015-07-06 model_description.tex
Moving table caps

A very simple way to represent this would be a game with two players, who both have two possible moves - ask for help, or not; and refer, or not (fig \ref{fig:simplest_game}). Since both parties are invested in the outcome of the pregnancy, we might allow them to share the same payoff if everything ends well. The only time things in this very restricted world obviously end poorly, is if the woman asks for help but does not get any. This implies that a rational player would always refer if asked for help, and is indifferent otherwise - in other words, there are three possible Nash equilibriums.

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=119mm]{figures/simplest_game}
\end{adjustbox}
\caption{A very simple two player game.}

\label{fig:simplest_game}
\end{figure}

@@

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=119mm]{figures/less_simple_game}
\end{adjustbox}
\caption{A less simple two player game.}

>>>>

A very simple way to represent this would be a game with two players, who both have two possible moves - ask for help, or not; and refer, or not (fig \ref{fig:simplest_game}). Since both parties are invested in the outcome of the pregnancy, we might allow them to share the same payoff if everything ends well.

\begin{figure}[H]
\sidecaption
\includegraphics[width=7cm]{figures/simplest_game}
\caption{A very simple two player game. The only time things in this very restricted world obviously end poorly, is if the woman asks for help but does not get any. This implies that a rational player would always refer if asked for help, and is indifferent otherwise - in other words, there are three possible Nash equilibriums.}
\label{fig:simplest_game}
\end{figure}

@@

\begin{figure}[H]
\begin{adjustbox}{center}
\includegraphics[width=78mm]{figures/less_simple_game}
\end{adjustbox}
\sidecaption{A less simple two player game.}
